\LARGE \bf A Teachable Robotic Agent for Children Learning Handwriting, Capable of Simulated Handwriting Itself

### 2014-11-14 rebuttal.txt

We would like to thank each of the reviewers for contributing such time and
their expertise to this review.

We address hereafter the reviewers' remarks.

The main weakness raised by the reviewers is the lacking literature review. We
acknowledge this weakness and we certainly appreciate and value the numerous
pointers provided by the reviewers. We propose to report on and situate ourselves amongst these
related works in the final version of the article.

While the application of the 'learning by teaching' paradigm to robotics is not
new (we did not intend to claim such a contribution, but we can
understand how the misunderstanding can arise from the second-last paragraph),
it appears that 'learning by teaching' a task requiring physical skills
(especially fine physical skills, as in handwriting) is still novel, and of particular significance for embodied
artifacts like robots.

Regarding the overall writing style of the paper, the points raised by
reviewer 1 are well taken and we appreciate the examples provided. We will
accordingly reword the article to match academic standards (including the
removal of overstatements like 'we have proven that...').

@@

The reviewers also raise several questions regarding the technical validation
of the system.

The characterization of the mistakes (like "global deformation" and "internal
proportion") comes from an existing report (reference [2]). We propose to make
an explicit reference to the classification methods used in this previous work
to classify and evaluate mistakes generated by our algorithm. We will also mention that the
 deformations have been directly (yet informally) validated
during a focus group with primary school teachers, prior to the studies.

Reviewer 1 also questions our assessment of generated letter models as being
"meaningful": The deformations are meaningful in the
sense that if a teacher wishes to create initial letters with a particular
feature (a 'd' with a large loop, for example), it is possible with this
system. We will clarify that it is the ability to create varied levels of
deformations which may be ascribed descriptive interpretations (not just
numerical) that is the desired outcome.

@@

Regarding the initial parameters used to generate wrong letters during the
validation studies, the values were drawn from a range chosen to generate
shapes for letters 'e' and 's' which would elicit correction. For the other
letters, parameters were fixed, generating shapes which some groups chose to
correct (e.g. 13/14 for 'n' and 2/14 for 'c').

The question whether the robot is believed to write by itself or not is a valid
concern. The question "Do you think Nao could write its name?", while it does
not directly check if the robot is believable, has been designed such as to
avoid putting words in the children's mouths (if we were to ask directly if the
robot's writing was believable). Our argument is that at no point in the
interaction did any child express that they did not believe that the robot was
writing itself, even in a situation where they could have said "well, it's not
*really* writing". We accept that we cannot conclude that the children believed
it was writing, and will reword the outcome to instead be that no child ever
expressed that they did not believe it was writing.

Reviewer 3 feels that the reporting of results is lacking academic
standards: while we do already provide the fundamental demographic data and
verification results, we have refrained from reading further into the data
because a full study with large sample sizes has yet to be completed. The work
presented was intended for verification of the technical soundness of the
system with children, in line with the 'enabling technologies' theme.

Finally, following the reviewers' suggestion, we propose to change the article
title: it was meant to re-purpose the idiom "Those who cannot do, teach" in the
context of children with handwriting difficulties having an opportunity to
improve through teaching. We appreciate this reviewer bringing to light the
potential for this to strike a nerve with teachers.

### 2014-11-27 rebuttal_sorted.txt

We agree that this was a wording issue on our part and will make reference to the classification methods used in previous work to determine such categories, and the confirmation that was received by teachers that the deformations are similar to childrens'.

>    (2) To assess whether the children believed that the letter-writing
>    trajectories shown on the tablet were being created by the robot, the
>    children were asked whether the robot could write its own name. This
>    question does not directly address believability, and there are plausible
>    interpretations of a “yes” answer that do not include the child
>    believing that the robot wrote what he or she saw on the tablet. For
>    instance, the child might think that the robot can write well but did not
>    actually write during the interaction. Thus, believability has not been
>    validated sufficiently. (Also, I recommend never saying that something is
>    generally “proven” when based on a limited sample.)

We agree with the points raised: it is a limitation of the question, which we imposed ourselves to avoid putting words in the children's mouths if we were to ask directly if the robot's writing was believable. Our argument is that at no point in the interaction did any child express that they did not believe that the robot was writing itself, even in a situation where they could have said "well, it's not *really* writing". We accept that we cannot conclude that the children believed it was writing, and will reword the outcome to instead be that no child ever expressed that they did not believe it was writing.

>    (3) “For example, for the model shown in Figure 1, the parameters may
>    represent the height of the top half of the letter compared to the bottom
>    half, the width of the overall shape, etc. Consequently, the shape
>    modelling process has produced the desired outcomes of parameterising the
>    shapes in ways which are able to be used to deform them meaningfully.”
>    - The author’s subjective appraisal of what variations are captured by
>    PCA is insufficient to claim the the deformations are meaningful.
>    Further, the word “meaningful” lacks grounding (what exactly does it
>    mean here)?
DONE
The deformations are meaningful in the sense that if a teacher wishes to create initial letters with a particular feature (a 'd' with a large loop, for example), it is possible with this system. We will clarify that it is the ability to create varied levels of deformations which may be ascribed descriptive interpretations (not just numerical) that is the desired outcome.
